\chapter{Introduction}
This is a action and strategy with often small adventures based game which can be played in single player as well as multi player mode. The single player modes is more of a Role Playing in which you will also computer assisted player whom you can command too along with you on your journey to greatness. Mulitplayer mode is however more strategy based, the game is a great enjoyment if in multi player there are around 15-20 players. In multiplayer also there is option of computer assisted players. In the single player mode, the game is AI assisted. The player can take up three basic roles :-\\
\begin{itemize}
\item Terrorist :- The terrorist is a person who will have his companions who will aim at winning over the treasuries of the city along with various minor targets like( dethroning  the ruling party or looting a bank, etc.). They will roam within the city as normal citizens and they will know only the people of their own contingent. Every terrorist will have some missions which they need to clear to win the treasury.
\item Army-man :- This person has been entitled by the city to protect it from  the terrorists. He has the right to kill any person within the city but if he kills any of the innocent person, his powers would decrease and after a certain limit he would  jailed/fined/deputed to some new place. They will only know the people of their own contingent.
\item Citizen :- The citizen is a broad category in which the person could be in any profession. He has to manage his profession along with the job of suspecting a person. He will have to report a terrorist to the police everyday and if he is correct, he will also get some magical powers but if he is wrong, his powers will be reduced/ he will be fined.
\end{itemize}
To make the game exciting, there are some special features like the witcher lady who could foresee the future of any person of the city and if anyone comes across her, would be facing the magical consequences. Not only this there would be some corrupt officials of the city who would support the terrorists for some benefits. Even the citizens who would be married, would be linked with their spouse. If anyone of the married pairs die, the other one would have die too. There would be healers roaming all around who could cure a person if offered money.